\begin{center}
	\textsc{Acknowledgments}
\end{center}
%
\noindent
%
I would like to express my heartfelt gratitude to all those who have helped me throughout my PhD journey. First and foremost, I am deeply grateful to my supervisors Pr. Engelbert Mephu Nguifo and  Dr. Jocelyn de Goër de Herve for their unwavering guidance, encouragement, and expertise throughout this research. Their constructive feedback and continuous motivation have been instrumental in shaping my ideas and refining my work. I am also indebted to Pr. Richard Emilion for his invaluable suggestions and help.


I would also like to thank my collaborators from the DAPPEM project, especially the members from INRAE and CHU Clermont-Ferrand, for their stimulating discussions, insightful feedback, and willingness to share their knowledge and expertise. Their contributions have enriched my work and broadened my perspective on the field. 


My heartfelt thanks go to the members of the Miners research team for constructive discussions and also for helping me out with non-academic activities. Their unconditional support made it possible for me to survive in a foreign country with a language barrier.


I would also like to extend my sincere gratitude to the members of the jury for agreeing to assess my work and providing constructive feedback.


I would like to express my heartfelt gratitude to my family and friends, for their mental support, unconditional love, and encouragement throughout this journey. Their belief in me and my abilities has been a constant source of inspiration and motivation, and I am grateful for their presence in my life.

This research was funded by the European Regional Development Fund, project DAPPEM–AV0021029. The DAPPEM project («Développement d’une APPlication d’identification des Erythèmes Migrants à partir de photographies»), was coordinated by Pr. Olivier Lesens and was carried out under the Call for Proposal ‘Pack Ambition Research’ from the Auvergne-Rhône-Alpes region, France. This work was also partially funded by Mutualité Sociale Agricole (MSA), France. I am immensely grateful for the financial assistance, which enabled me to carry out my research with the necessary resources and facilities.

            
I am deeply appreciative of the contributions of all those who have helped me along the way, and I am proud to have had the opportunity to work with such talented and dedicated individuals.


Finally, I am grateful to the almighty for showering his blessing on me.